---
title: "Developing Data Products Week 4: Shiny Application and Reproducible Pitch"
author: "xbuRAw (GH)"
date: "December 30, 2019"
geometry: margin=2cm
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = TRUE, warning = FALSE, message = FALSE)
```

<style>
slides > slide {
  overflow-x: auto !important;
  overflow-y: auto !important;
}
slides > slide:not(.nobackground):after {
  content: '';
}
</style>

## Introduction
 - This presentation is part of final project of the Developing Data Products course.
 - It contains a short pitch and supplementary information about the shiny app that was also build as part of the project.
 - The presentation was written in the *R Markdown* language in conjunction with the [ioslides](https://bookdown.org/yihui/rmarkdown/ioslides-presentation.html) framework and compiled with [RStudio](<https://www.rstudio.com>).
 - Note: some slide are scrollable.
 - Links: [project: presentation](https://xburaw.github.io/ds-course9-project-w4/presentation.html) / [project: shiny web app](https://xburaw.shinyapps.io/shinyapp/)

## Application
 - The main focus of the project was to develop a [shiny](https://shiny.rstudio.com/) application. The shiny web app has the title **C9W4: ShinyApp Project** and is hosted at [shinyapps.io](https://www.shinyapps.io/).
 - The *shiny* framework is a complete suite to create web apps in the R language and is therefore very useful for data analysts already versed in R.
 - The application has three parts:
    1. A exploratory part where the data set can be analysed via different interactively requested plots.
    2. A trained random forest model can be used to make predictions for the MPG (miles per gallon) of a car based on interactivly adjusted parameters.
    3. Documentation and other helpful information about the app can be found in the Documentation tab of the app.
 - The source code for the web application is hosted in [this repository](https://github.com/xbuRAw/ds-course9-project-w4) on github. And consists out of the files `ui.r`, `server.r` and `modelRF.r` in the `/shinyApp` folder.
  
## Dataset
The [mtcars](https://www.rdocumentation.org/packages/datasets/versions/3.6.1/topics/mtcars) data set
is part of the base R package and consists of 32 observations of 11 variables (properties of different cars).
Originally the data was extracted from the Motor Trend US magazine in 1974.  
* Henderson & Velleman, Building Multiple Regression Models Interactively (1981)"  

A short overview of the structure of the dataset:

```{r}
str(mtcars)
```
## Prediction
I chose a random forest prediction algorithm because of its relative simplicity and high accury it delivers, while still being performant.  
The goal for the model is to accuratly predict the `mpg` variable using the rest of the variables as predictors. Using cross validation the model is trained on the whole data set.

```{r echo = FALSE}
library(caret)
set.seed(111)
```
A short summary of the trained model can be seen in the output of the following cell.

```{r}
# the training function
rfTrain <- function() {
  return(
    train(mpg ~ ., data = mtcars, method = "rf",
      trControl = trainControl(method = "cv", number = 10)
    )
  )
}

# the prediction function 
rfPredict <- function(model, carParameters) {
  prediction <- predict(model, newdata = carParameters)
  return(prediction)
}

rfTrain()
```

## Thank you
Have a nice day!  

xbuRAw(GH), December 2019